---
title: "Mapping the American Dream"
# author: "by Guillermo Gomez"
# date: 2018-05-19
# output: html_document
output: 
  github_document:
    toc: true
    toc_depth: 6
---

```{r setup, include=FALSE, eval = TRUE, echo = FALSE, message = FALSE, warnings = FALSE}
# knitr options
knitr::opts_chunk$set(echo = FALSE, out.width = "100%", dpi = 500, message = FALSE, warnings = FALSE)
```

```{r, eval = TRUE, echo = FALSE}
library(tidyverse, quietly = TRUE)
library(haven, quietly = TRUE)
library(sf, quietly = TRUE)

# Parameters
# Commuting zones in Alaska and Hawaii
CZS_AK_HI <- c(
  "34101",
  "34102",
  "34103",
  "34104",
  "34105",
  "34106",
  "34107",
  "34108",
  "34109",
  "34110",
  "34111",
  "34112",
  "34113",
  "34114",
  "34115",
  "34701",
  "34702",
  "34703",
  "35600"
)

# Albers projection for 48 contiguous US states
US_ALBERS <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +datum=WGS84 +no_defs"

# Colors used in New York Times map
NYT_COLORS <- c(
  "#740023",
  "#b63132",
  "#d27952",
  "#e9b777",
  "#fdf6a3",
  "#a2c0a1",
  "#55889e",
  "#195473",
  "#004364"
)

# Color used in New York Times map for missing values
NYT_NA_COLOR <- "#f2f2f2"

# Population URL: 
# https://factfinder.census.gov/faces/tableservices/jsf/pages/productview.xhtml?src=bkmk

# Jobs by educational attainment data: ACS_16_5YR_S2301

# Monthly housing costs by income, ACS DP04

# Ethnic diversity by county: ACS_16_5YR_B03002

# solution-begin
# Load dataset with mobility by county
mobility_dta_file <- "D:/c01 Data/online_table2.dta"

# Load employment by educational attainment data
jobs_file <- "D:/c01 Data/ACS_16_5YR_S2301_jobs/ACS_16_5YR_S2301.csv"

# DP04 MONTHLY HOUSING COSTS
housing_file <- "D:/c01 Data/ACS_16_5YR_DP04_housing/ACS_16_5YR_DP04.csv"

# Ethnic diversity by county
diversity_file <- 
  "D:/c01 Data/ACS_16_5YR_B03002_race/ACS_16_5YR_B03002.csv"

population_file <- "D:/c01 Data/PEP_2016_PEPANNRES/PEP_2016_PEPANNRES.csv"



# Geographic boundaries as used by Raj Chetty
states_rds <- "D:/R/cb_2015_us_state_20m_sf.rds"
counties_rds <- "D:/R/cb_2015_us_county_20m_sf.rds"
# solution-end
```


# A Data Visualization of Opportunity in America
In 1931, the writer James Truslow Adams first proposed the term "the American Dream" in his book, to refer to the ideal "dream of a land in which life should be better and richer and fuller for everyone, with opportunity for each according to ability or achievement."

Since then, others have attempted to define what the American Dream means, and come up with different interpretations. One famous and yet tragic version of this comes from protagonist Willy Loman in Arthur Miller's Death of a Salesman. His view that charisma and charm alone can open up opportunity and lead to prosperity both captures the imagination of the everyman reader and leads to self-destruction, as this American Dream does not hold up. I stay true to Adams' original intention and attempt to define a robust interpretation, one that we can all live by.
My analysis should not be seen as a definitive guide for a low-income family looking to move to optimize for their kids' future, but rather as a conversation-started highlighting available data in a novel way. I hope primarily to add to the national conversation on opportunity and the American Dream. 
This project aims to map US counties which today best represent this definition of the American Dream and would be of interest to a low-income or middle-class family with children. I interpret Adams' statement to refer to four key metrics.

*Intergenerational income mobility: Adams claims "life should be better and richer and fuller for everyone"; fuller than what, we must ask? Fuller than the past, of course. We all hope that kids have a higher standard of living than their parents. I look at data from the Equality of Opportunity Project, run by Stanford economist Raj Chetty and Harvard economist Nathaniel Hendren, on the causal income mobility for children who move to a new county. This data estimates by how much that child's adult income would increase for every year spent in a different county. Some counties are better for children to grow up in than others, as per their data. The study claims that "counties with less concentrated poverty, less income inequality, better schools, a larger share of two-parent families, and lower crime rates tend to produce better outcomes for children in poor families." 
Opportunity: "with opportunity for each according to ability " I define the American dream as the ability to access and live out opportunities for intra- and intergenerational advancement through hard work, even given only a high school education. 

* Affordability: "life should be better and richer ... for everyone." This implies broad accessibility beyond economic barriers. I do this analysis for the families at the 25th percentile of income, the family solidly below middle class, and look at the costs of a home mortgage as a fraction of monthly income. 
* Community:  "For everyone" implies a welcoming environment and community. I also define the American dream as the ability to live in a community where one is welcome and not culturally or linguistically isolated, so that opportunity can be practically accessed by anyone, without barriers to identity. This ideal is more difficult to translate into a metric, and may not be of similar interest to all demographics and families. I choose a proxy for ethnic diversity, the complement (one minus) the percentage of individuals who are white, non-Hispanic. I explain the reasoning for this in my methodology. 

You may find that this definition is incomplete, or you may find that you value certain aspects of this definition of the American dream above others. This project leaves some flexibility for more personalized definitions of the American dream, by allowing for different weights on each of the four factors I consider. 

## Methodology

*Intergenerational income mobility: The effects of moving to a better county accumulate during childhood but persist into adulthood, Chetty and Hendren's findings show. Thus, moving to a county with a higher score positively impacts children's adult income earning mobility well into adulthood. This effect is bigger for low-income children, those in the 25th percentile of family income, than for richer children (75th percentile), but both benefit from moving to a better county. The negative tail end of the adult income increase estimates for the 75th percentile kids is longer than the positive tail end, implying that there is a possibility for some higher-income kids that moving will be worse than staying. I choose to look only at poorer families, the 25th percentile. I assume the factors which go into calculating these increased income effects are loosely related to the other factors I measure, and so I am not plotting the same data through multiple proxies. 

*Opportunity: To account for the the importance of jobs in the American dream, I researched labor force participation rates for all adults aged 25 to 64 with a high school degree (or equivalent), or less. This is a close proxy, I argue. I calculated this participation rate and ranked all counties by it, such that counties which scored high had a large labor participation rate among residents with a high school education or less while counties which scored poorly had high unemployment rates for the same demographic, either because there are few jobs or because the jobs available require higher levels of education.

*Affordability: I look at housing costs as a fraction of income to rank counties by how affordable they are to buy a house in. The dataset for these metrics comes from DP04 in the 2016 ACS 5-Year Survey. I calculate the costs of a mortgaged home and not a rental because I assume the American dream includes homeownership. I calculate the percentage of these costs which fall below 29.9% of monthly income for residents, something the ACS already calculates. I choose this monthly cost percentage cutoff based on the rule of thumb that one should not spend more than 30% of income on housing. I look only at counties with more than 500 homes, as anything less would likely lack the infrastructure and amenities most people assume in their communities.  

*Community and ethnic diversity: I choose the complement of the percentage white, non-Hispanic residents as a proxy for ethnic diversity because many counties which are affordable and may offer income mobility are strongly homogenous according to the ACS data. Conceivably, a family of a non-White background who chooses to move there might want to find other families to connect with in a religious or cultural context, as community leads to a richer, more fulfilling community life. I believe people can connect genuinely in many ways and that America is already a melting pot; as such, I recommend a low weighting of this factor.  





I expand work from the Equality of Opportunity Project, which looks at how location and the environment in which children grow up affects intergenerational income mobility. This data has been visualized in this NY Times article, and published in the following paper. Children who move to "better" counties see a causal rise in their annual adult incomes; the effect outlasts the location, such that even after children leave the better county they'd moved to, their adult incomes are still likely to be higher. I combine this data with various key metrics on employment and jobs, affordability, and ethnic diversity, using the American Community Survey. 

I also incorporate the following datasets from the American Community Survey, using only 5-year estimates from 2016:

**Monthly housing costs, "ACS_16_5YR_DP04"
**Ethnic makeup by county, "ACS_16_5YR_B03002"
**Employment by educational level, "ACS_16_5YR_S2301"








## Effects of Neighborhoods on Intergenerational Mobility, County-Level Estimates

The effects of moving to a better county accumulate during childhood but persist into adulthood, RAj Chetty's findings show. Thus, moving to a county with a higher score positively impacts children's adult income earning mobility well into adulthood. This effect is bigger for low-income children (those in the 25th percentile of family inccome) than for richer children (75th percentile), but both benefit from moving to a better county. The negative tail end of the adult income increase estimates for the 75th percentile kids is longer than the positive tail end, implying that there is a possibility for some higher-income kids that moving will be worse than staying. 


# Read mobility data set, examine the data
```{r, q1, eval = TRUE, echo = FALSE}
# solution-begin
mobility_dta <- 
  read_dta(mobility_dta_file) 

mobility <-
  mobility_dta %>%
  mutate(
    pct_kids_p25 = pct_causal_p25_kr26,
    pct_kids_p75 = pct_causal_p75_kr26, 
    county = cty2000, 
    county_stateabbrv = str_c(county_name, stateabbrv, sep = " County, ")
  ) 

# mobility %>%
#   ggplot(aes(pct_kids_p25)) +
#   geom_histogram(bins = 20, fill = "green") +
#   theme_minimal() +
#   labs(
#     title = "Distribution of Adult Income Mobility by County, Causal Estimates", 
#     subtitle = "For Families at the 25% Percentile of Income and with Kids",
#     x = "Causal Income Mobility Estimate (% Increase)", 
#     y = "Frequency",
#     caption = "Source: Raj Chetty"
#   )
# 
# mobility %>%
#   ggplot(aes(pct_kids_p75)) +
#   geom_histogram(bins = 20, fill = "blue") +
#   theme_minimal() +
#   labs(
#     title = "Distribution of Adult Income Mobility by County, Causal Estimates", 
#     subtitle = "For Families at the 75% Percentile of Income and with Kids",
#     x = "Causal Income Mobility Estimate (% Increase)", 
#     y = "Frequency",
#     caption = "Source: Raj Chetty"
#   )
# # solution-end
```



```{r, q2, eval = TRUE, echo = FALSE}
# solution-begin
# Ignore Alaska and Hawaii, not practical to move there
counties <-
  read_rds(counties_rds) %>%
  mutate(county = as.numeric(GEOID)) %>% 
  filter(!str_detect(STATEFP, "02")) %>%
  filter(!str_detect(STATEFP, "15")) %>%
  st_transform(crs = US_ALBERS)

states <- 
  read_rds(states_rds) %>%
  filter(!str_detect(STATEFP, "02")) %>%
  filter(!str_detect(STATEFP, "15")) %>%
  mutate(county = as.numeric(GEOID)) %>%
  st_transform(crs = US_ALBERS)

# Merge counties with geographic data and change to Albers projection
mobility_county <-
  mobility %>%
  filter(stateabbrv != "AK", stateabbrv != "HI") %>%
  left_join(counties, by = "county") %>%
  select(county, county_stateabbrv, pct_kids_p25, geometry)
# solution-end
```

I want to visualize the income mobility data for the 25th-percentile family in particular, and I focus on this in all subsequent analyses. 

# Visualize causal estimates
```{r, q3, eval = TRUE, echo = FALSE}
# solution-begin
q3 <- 
  mobility_county %>%
  ggplot() +
  geom_sf(aes(fill = pct_kids_p25), color = NYT_NA_COLOR, size = 0.01) +
  geom_sf(data = states, fill = NA, size = 0.01) +
  scale_fill_gradientn(
    colors = NYT_COLORS,
    na.value = NYT_NA_COLOR
  ) +
  coord_sf(datum = NA) +
  guides(
    fill = guide_colorbar(
      title = "Average Adult Annual Income Change (%)",
      title.position = "top",
      title.theme = element_text(size = 8, angle = 0),
      title.hjust = .5,
      label.theme = element_text(size = 7, angle = 0),
      barwidth = 12,
      barheight = 0.4,
      direction = "horizontal"
    )
  ) +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 6)
  ) +
  labs(
    title = "The Effects of Location on Intergenerational Adult Income Mobility",
    subtitle = "Change in Annual Earnings for 25th Percentile Families with Kids"
  ) +
  scale_fill_gradientn(
    breaks = c(-1.5, -1.0, -0.5, 0, .5, 1.0, 1.5, 2.0),
    colors = NYT_COLORS,
    na.value = NYT_NA_COLOR
  ) 

q3 

# solution-end
```

Here are a few observations on the data displayed in this map. 
Native reservations show the most negative income mobility. 
Mobility seems greatest in the upper midwest. The border regions of the Southeast are neutral, the deep south is highy negative. Silicon Valley is not that positive, rather a bit below the median. 
The Dakotas are highly mobile in some parts but overall very empty. There may be an influence from the oil and gas industry in making some of these counties appear as if they have highly-mobile incomes. Wyoming and Utah are lit up blue, which is surprising. Nevada also fares pretty well. 
The Northeast is above average but not in the metropolitan areas. Pennsylvania seems to do better than urban zones. 
Iowa and Minnesota do well throughout. 
The Central Valley does poorly, below avergae for the country. 
There is lots of missing data down the middle of the country, visualized by the blank counties. 

Looking at the top ten best and worst counties, we can learn a lot more. 

```{r, eval = TRUE, echo = FALSE}
# solution-begin
population <- 
  read_csv(population_file) %>%
  filter(!str_detect(`GEO.display-label`, "Alaska"),  !str_detect(`GEO.display-label`, "Hawaii")) %>%
  mutate(
    county = as.numeric(GEO.id2), 
    county_state = `GEO.display-label`, 
    pop_2016 = respop72016
  ) %>%
  select(county, county_state, pop_2016)

mobility_county %>%
  top_n(10, wt = pct_kids_p25) %>%
  left_join(population %>% select(-county_state), by = "county") %>%
  select(county_stateabbrv, pct_kids_p25, pop_2016) 

mobility_county %>%
  top_n(-10, wt = pct_kids_p25) %>%
  left_join(population %>% select(-county_state), by = "county") %>%
  select(county_stateabbrv, pct_kids_p25, pop_2016) 
# solution-end
```

The best-performing counties are outliers, it seems, as whatever happens in these counties is exceptional. Iowa and the Dakotas do well. 

The worst-performing counties have native reservations or are in the deep south. Most are small in population, though population alone is not correlated with higher mobility. Missouri has three counties in this list. The counties tend to be majority of one race or ethicity. Some appear to be nearly empty unincorporated towns (Humphreys) or counties (Menominee is the least populous county in Wisconsin). 


```{r, eval = TRUE, echo = FALSE}
# task-begin
chloroplether <- 
  function(data, var_fill, title_main, subtitle, title_legend, caption) {
    # Your code here
    
    # return(chloro_plot)
  }

# task-end

# solution-begin
chloroplether <- 
  function(data, var_fill, title_main, subtitle, title_legend, caption) {
    var_fill <- enquo(var_fill)
    chloro_plot <-
      data %>%
      ggplot() +
      geom_sf(aes(fill = data %>% pull(!!var_fill)), color = NYT_NA_COLOR, size = 0.01) +
      geom_sf(data = states, color = "black", fill = NA, size = 0.01) +
      scale_fill_gradientn(
        colors = NYT_COLORS,
        na.value = NYT_NA_COLOR
      ) +
      coord_sf(datum = NA) +
      guides(
        fill = guide_colorbar(
          title = title_legend,
          title.position = "top",
          title.theme = element_text(size = 8, angle = 0),
          title.hjust = .5,
          label.theme = element_text(size = 7, angle = 0),
          barwidth = 12,
          barheight = 0.4,
          direction = "horizontal"
        )
      ) +
      theme_void() +
      theme(
        legend.position = "bottom",
        legend.text = element_text(size = 6)
      ) +
      labs(
        title = title_main,
        subtitle = subtitle,
        caption = caption
      )
    
    return(chloro_plot)
  }
# solution-end
```

To account for the the importance of jobs in the American dream, I researched labor force participation rates for all adults aged 25 to 64 with a high school degree (or equivalent), or less. I calculated this participation rate and ranked all counties by it, such that counties which scored high had a large labor participation rate among residents with a high school education or less while counties which scored poorly had high unemployment rates for the same demographic, either because there are few jobs or because the jobs available require higher levels of education.    

```{r, eval = TRUE, echo = FALSE}
# solution-begin
# Jobs by educational attainment
jobs <- 
  read_csv(
    jobs_file,
    na = c("(X)", "-", "**", "N")
  )

jobs_county <-
  jobs %>%
  filter(!str_detect(`GEO.display-label`, "Alaska"),  !str_detect(`GEO.display-label`, "Hawaii")) %>%
  mutate(
    county = as.numeric(GEO.id2), 
    county_state = `GEO.display-label`,
    employrate = (HC01_EST_VC44 + HC01_EST_VC45) / HC01_EST_VC43 * 100
  ) %>%
  left_join(counties, by = "county") %>%
  select(
    county, 
    county_state, 
    employrate,
    geometry
  ) %>%
  ungroup()


# HC02_EST_VC44	Labor Force Participation Rate; Estimate; EDUCATIONAL ATTAINMENT - Population 25 to 64 years - Less than high school graduate

# HC02_EST_VC45	Labor Force Participation Rate; Estimate; EDUCATIONAL ATTAINMENT - Population 25 to 64 years - High school graduate (includes equivalency)

q4.2 <-
  chloroplether(
    data = jobs_county,
    var_fill = employrate,
    title_main = "Labor Participation Rate with High School Education or Less",
    title_legend = "Rate (%)",
    subtitle = "For Adults Aged 25 - 64 of all Genders and Races",
    caption = "Source: ACS 5-Year Surveys"
  )

q4.2


jobs_county %>%
  top_n(10, wt = employrate) %>%
  left_join(population %>% select(-county_state), by = "county") %>%
  transmute(county_state, labor_participation_rate = employrate, population2016 = pop_2016) 

jobs_county %>%
  top_n(-10, wt = employrate) %>%
  left_join(population %>% select(-county_state), by = "county") %>%
  transmute(county_state, labor_participation_rate = employrate, population2016 = pop_2016)  
# solution-end
```

Looking at the map above and the top ten best and worst counties for employment given low educational attainment, I can conclude that certain highly-educated counties do not offer much employment to those with high school education or less. The counties with the lowest barrier to entry for jobs are in the South and rural Appalachia. 

Limitations: This data does not imply causation, and does not indicate that a new arrival would do as well. 
Again, the rural South and native reservations do poorly. However, we may also be fooled by counties with low populations. 

Now, counties which are highly agricultural or have oil/gas jobs don't fare as well. The border region of Texas and Louisiana do very well, and the American South does well, too.  


## Housing Costs
I look next at housing costs as a fraction of income to rank counties by how affordable they are to buy a house in. The dataset for these metrics is DP04 from the ACS 5-Year Survey completed in 2016. I calculate the costs of a mortgaged home (and not a rental because I define the American dream as including homeownership) and calculate the percentage of these costs which fall below 29.9% of monthly income for residents. 

I choose the monthly cost percentage cutoff based on the rule of thumb that one should not spend more than 30% of income on housing, see (http://fortune.com/2015/08/04/housing-30-percent-rule/). We specifically look at costs for homes with a mortgage and not rental rates or otherwise because we define the American dream as including home ownership, and so want to reflect how feasible that would be.


```{r, eval = TRUE, echo = FALSE}
# solution-begin
housing_data <- 
  read_csv(
    housing_file, 
    na = c("(X)", "-", "**", "N")
  ) 

housing_county <-
  housing_data %>%
  filter(HC01_VC159 > 500) %>%
  rowwise() %>%
  mutate(
    county = as.numeric(`GEO.id2`), 
    county_state = `GEO.display-label`,
    `pct_below_29.9` = sum(HC01_VC160, HC01_VC161, HC01_VC162)  / HC01_VC159 * 100
  ) %>%
  ungroup() %>%
  left_join(counties, by = "county") %>%
  select(county, county_state, `pct_below_29.9`, geometry) %>%
  filter(!is.na(`pct_below_29.9`)) %>%
  arrange(`pct_below_29.9`)


q4.3 <-
  chloroplether(
    data = housing_county,
    var_fill = `pct_below_29.9`,
    title_main = "Housing Affordability as a Share of Income",
    title_legend = "Mortgaged Housing Units considered Affordable (%)",
    subtitle = "Percentage of Mortgaged Units costing under 29.9% of Monthly Income",
    caption = "Source: ACS 5-Year Surveys"
  )

q4.3
# solution-end
```

The midwest and Nevada fare well, and the middle of the country in general does well. 
California in particular and the West in general do poorly due to high housing costs. California and parts of the NE do the worst. 

This map does not factor in population to account for demand for housing, but it does so indirectly by looking at the costs of housing relative to income. 

Very cheap housing might suggest a ghost town. Perhaps we want something in the middle of the affordability index, as there might be limitations to valuing "ghost towns" so highly. 

Some things to think about: Counties have great variation in affordability even within them; expensive counties might have higher-paying jobs, some affordable housing projects, lower taxes, etc. Feel free to do any additional exploratory data analysis.

## Ethnic diversity
You can see from the previous datasets on income mobility and jobs that opportunity is found more in the Midwest and rural areas agricultural areas. It's possible some of these counties are not very diverse. We want to extend our analysis so that we take into account diversity as it may be important to the "American Dream" for immigrant families, or families which consider themselves of minority ethnic backgrounds. If the families who care most about the analysis you're doing are not white and would feel culturally or linguistically isolated if they moved to a predominantly-white county, we want to give some consideration to diversity levels. How important this is depends on the family of course.

Below I plot the percentage of a county's population that is white, non-Hispanic. To simplify this analysis, I define diversity as the complement of this percentage. A county with 100% white, non-Hispanic demographics would be 0% diverse; one with a 70% white demographic is 30% diverse. There are many limitations to using this definition of diversity and so I weight this metric lightly in combining it with the other data on mobility, jobs, and housing.  

```{r, eval = TRUE, echo = FALSE, message = FALSE, warnings = FALSE}
# solution-begin
# Ethnicity 
diversity_data <- 
  read_csv(
    diversity_file, 
    na = c("(X)", "-", "**", "N")
  ) 

diversity_county <-
  diversity_data %>%
  filter(!str_detect(`GEO.display-label`, "Alaska"),  !str_detect(`GEO.display-label`, "Hawaii")) %>%
  mutate(
    county = as.numeric(GEO.id2), 
    county_state = `GEO.display-label`,
    pct_white = HD01_VD03 / HD01_VD01 * 100, 
    diversity = 100 - pct_white
  ) %>%
  left_join(counties, by = "county") %>%
  select(county, county_state, pct_white, diversity, geometry) 
# solution-end
```



```{r, eval = TRUE, echo = FALSE}
# solution-begin
chloroplether(
  diversity_county, 
  pct_white,
  title_main = "Percentage White non-Hispanic Demographic by County" , 
  subtitle = "",
  title_legend = "Percentage of County Population", 
  caption = "Source: ACS"
)
# solution-end
```

Some parts of the country are very white. Some of these counties are counties that have ranked highly in previous analyses. It's possible these counties will not be good fits for families who might be more comfortable with some diversity.   


# American Dream Index

I now combine all four data sets into what I call the "American Dream Index." I normalize the percentage estimates from Raj Chetty's income mobility data to be from 0 to 100% instead of -2 to +2% annual income gain based on the minimum and maximum values of this range. The 100% represents the most adult income-boosting county, and 0% represents the worst (with the greatest annual adult income decline). This will let me compare all the data I've looked at as percentages. The American dream is a flexible concept and there is no one definition. Given the data I've used and the assumptions I've made, there is much room for interpretation. I choose to weight the factors I've analyzed as follows:

* the effect of county on children's adult income mobility: 45% weight
* percent of homes costing less than 29.9% of monthly income, by county: 25%
* labor participation rate for adults with a HS education or less: 25%
* ethnic diversity [0% diverse is all white, to 100% diverse is not white]: 5%


```{r, eval = TRUE, echo = FALSE, message = FALSE, warnings = FALSE}
# solution-begin
merged_data <-
  mobility_county %>% 
  select(-county_stateabbrv) %>%
  left_join(jobs_county %>% select(-geometry), by = c("county")) %>%
  left_join(housing_county %>% select(-geometry), by = c("county", "county_state")) %>%
  left_join(diversity_county %>% select(-c(geometry, county_state, pct_white)), by = "county") %>%
  filter(!is.na(`pct_below_29.9`), !is.na(diversity)) %>%
  mutate(
    gross_rank = row_number(),
    pct_kids_p25 = pct_kids_p25 / max(pct_kids_p25) * 100
  ) %>%
  arrange(desc(pct_kids_p25, diversity), employrate, `pct_below_29.9`) %>%
  select(county, county_state, pct_kids_p25, employrate, `pct_below_29.9`, diversity, geometry) 
# solution-end
```


```{r, eval = TRUE, echo = FALSE}
# solution-begin
weight_calc <- function(w1, w2, w3, w4) {
  c(w1, w2, w3, w4) / sum(w1, w2, w3, w4)
}

weights <- weight_calc(0.45, 0.25, 0.25, 0.05)
# solution-end
```

```{r, eval = TRUE, echo = FALSE}
# solution-begin
weights <- weight_calc(0.45, 0.25, 0.25, 0.25)

merged_data <-
  merged_data %>%
  rowwise() %>%
  mutate(
    weighted_rank = pct_kids_p25 * weights[1] + 
      employrate * weights[2] +
      `pct_below_29.9` * weights[3] +
      diversity * weights[4]
  ) %>%
  arrange(desc(weighted_rank))

merged_data %>% 
  top_n(10, wt = weighted_rank)

merged_data %>% 
  top_n(-10, wt = weighted_rank)
# solution-end
```

## Mapping the American Dream Index
```{r, eval = TRUE, echo = FALSE}
merged_data %>%
  write_csv("merged_data.csv")


```


```{r, eval = TRUE, echo = FALSE}
# solution-begin
p <- chloroplether(
  merged_data, 
  weighted_rank,
  title_main = "Mapping the American Dream Index" , 
  subtitle = "A County Ranking by Income Mobility, Accessible Jobs\nAffordable Housing, and Ethnic Diversity",
  title_legend = "Personalized American Dream Index (%)", 
  caption = "Source: Raj Chetty Lab, ACS 5-Year Surveys"
)
# solution-end
```





```{r, eval = TRUE, echo = FALSE, message = FALSE, warnings = FALSE}
merged_data %>%
  top_n(10, wt = weighted_rank) %>%
  left_join(population %>% select(-county_state), by = "county") %>%
  select(county_state, weighted_rank, pop_2016) 

merged_data %>%
  top_n(-10, wt = weighted_rank) %>%
  left_join(population %>% select(-county_state), by = "county") %>%
  select(county_state, weighted_rank, pop_2016) 

merged_data %>%
  write_csv("merged_data.csv")
```


The American dream is strongest in a handful of counties. There is a strong pattern here which agrees with anecdotal evidence I've heard about where families are moving to. We could expand this analysis by looking at where people are actually moving from and to. 
Smaller counties are better for the American dream overall. The highest-scoring counties are the smallest. 

```{r}
library(datamaps)
options(stringsAsFactors = F)
ichoropleth(Crime ~ State,
            data = violent_crime,
            pal = `PuRd`, 
            animate = "Year"
            )


```
